Data Cleaning

### 2023-03-08 modeling_data/GLOBI_bee_update_clean.Rmd
more reformatting

## Combine
```{r}
# Combine without dropping duplicates
# The filtering method guarantees two disjoint data frames
interactions_dup = rbind(bee_source_df, plant_source_df) 
# Combine and drop duplicates
interactions = rbind(bee_source_df, plant_source_df) %>% unique()
```

# Export to csv file
```{r}
# readr::write_csv(interactions, "interactions-14dec2022.csv")
```

>>>>

## Combine
```{r}
# Combine without dropping duplicates
# The filtering method guarantees two disjoint data frames
interactions_dup = rbind(bee_source_df, plant_source_df) 
# Combine and drop duplicates
interactions_b = rbind(bee_source_df, plant_source_df) %>% unique()
```

## Reformat column names
```{r}
for (c in colnames(interactions_b)) {
  interactions_b[[c]] <-  tolower(interactions_b[[c]])
}

capitalize = function(a_string){

  beginning = toupper(substr(a_string,1,1))
  ending = substr(a_string,2,nchar(a_string))

  return(paste0(beginning,ending))

}

## Remove plants not id'd to at least genus level, and bees that are not id'd to species
## Change old family names for Asteraceae, Lamiaceae and Apiaceae
```{r}
#reformat the interactions data:
interactions_reformat = interactions_b %>% 
  mutate(scientificName = capitalize(sourceTaxonSpeciesName), 
         bee_family = capitalize(sourceTaxonFamilyName),
         plant_family = capitalize(targetTaxonFamilyName), 
         plant_genus = capitalize(targetTaxonGenusName),
         plant_species = capitalize(targetTaxonName)) %>%
  filter(scientificName != '' & plant_family !='' & plant_genus != "") %>%
  filter(targetTaxonRank %in% c('subspecies','species',"genus",'subgenus','variety')) %>%
  filter(sourceTaxonRank %in% c("subspecies",'variety','species')) %>%
  mutate(plant_family = ifelse(plant_family=='Compositae','Asteraceae',plant_family)) %>%
  mutate(plant_family = ifelse(plant_family=='Umbelliferae','Apiaceae',plant_family)) %>%
  mutate(plant_family = ifelse(plant_family=='Labiatae','Lamiaceae',plant_family)) 
```

# Export to csv file
```{r}
# readr::write_csv(interactions_reformat, "interactions-14dec2022.csv")
```
